### 2014-12-04 fundamentals/impl.tex
adding DRE acronym

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and multiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the 
implementation of the region-institution-facility heirarchy. 
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \TODO{DRE}.
Support for users and developers via the Cycamore library of
agents \TODO{archetypes?} and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.
These features provide a solid foundation on which to build an interconnected community 
of archetype developers with diverse backgrounds and simulation goals.

@@

In addition to the core functionality of the \Cyclus kernel, which is focused on
the set of capabilities needed to implement an agent-based simulation
with dynamic resource exchange, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed part of \Cyclus, with a primarily forward-looking
focus on supporting interesting \textit{in situ} metric analysis tools.

>>>>

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and multiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the 
implementation of the region-institution-facility heirarchy. 
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the Cycamore library of
agents \TODO{archetypes?} and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.
These features provide a solid foundation on which to build an interconnected community 
of archetype developers with diverse backgrounds and simulation goals.

@@

In addition to the core functionality of the \Cyclus kernel, which is focused on
the set of capabilities needed to implement an agent-based simulation
with \gls{DRE} a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed part of \Cyclus, with a primarily forward-looking
focus on supporting interesting \textit{in situ} metric analysis tools.
